---
title: "Assignment 2, Task 2"
author: "Catherine Takata"
date: "2/7/2021"
output: html_document
---

### Overview
Data source: Abrahamson, W.G. 2019. Survival, growth and biomass estimates of two dominant palmetto species of south-central Florida from 1981 - 2017, ongoing at 5-year 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(GGally)
library(broom)
library(jtools)

```

```{r}
# Read in data set locally 

palmetto <- read_csv(here("data", "palmetto.csv"), 
                     col_types = cols(.default = 'c')) %>% 
  mutate(height = as.numeric(height))
```


```{r}
# Data wrangle to isolate specified variables 

palmetto_species <- palmetto %>% 
  select(species, height, length, width, green_lvs) %>% 
  mutate(species = factor(species)) %>% 
  mutate(length = as.numeric(length)) %>% 
  mutate(width = as.numeric(width)) %>% 
  mutate(green_lvs = as.numeric(green_lvs))
  
```

A section containing 2 - 3 finalized data visualizations (with figure captions) in which you explore differences in height, canopy length, canopy width, and green leaves for the two species. Add a figure caption to each. Below each data visualization, add a short (~1 sentence) statement with a takeaway from the visualization.

```{r}
ggplot(data = palmetto_species, aes(x = height, y = length)) + 
  geom_point(aes(color = species))

ggplot(data = palmetto_species, aes(x = height, y = width)) +
  geom_point(aes(color = species))
```

A section in which you perform binary logistic regression using plant height, canopy length, canopy width and green leaves as predictor variables to understand how they relate to probability of a plant being Serenoa repens or Sabal etonia 


```{r}

```













